Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-26 ms.tex
Update on Overleaf.

\begin{abstract}
\textit{Will complete at end}
%{\bf Ignore: Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars. Applying a local prescription for this pre-supernova feedback can be sufficient in matching star formation rates in a simulation with full radiative transfer on short timescales. However, the long-range effects of ionizing radiation are important in producing a volume-filling diffuse, warm-ionized medium in the ISM and in the disk-halo interface. This is essential for allowing supernovae to drive significant gas outflows that travel throughout and beyond the virial radius of the galaxy. A simulation with local radiation feedback only is unable to drive significant outflows as the supernovae are trapped well within the inner halo by higher density cold and warm neutral gas.}
\end{abstract}

>>>>

% Letter word count:
%    Text (including captions) : 3500
%    Abstract                  : 500
%    # Figures                 : 5
%       max panels per fig     : 9
%    # references              : 50

\begin{abstract}
%
%
% NOTE: Overleaf includes abstract words in word count in text... subtract
%       this from the total.
%
%
Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution. Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe. However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium. As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars. In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis. By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy. We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is a necessary component to drive outflows in our galaxy. In addition, we find that a localized approximation for radiation feedback is sufficient to reduce the star formation rate but, importantly does not drive significant outflows. Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
\end{abstract}
